A Domain Specific Language for SpectreGuard

### 2020-12-09 paper/main.tex
More explanation of the analysis

\begin{figure}
  \centering
\resizebox{0.67\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
  \openup 3mm
\begin{gather*}
  \inference{}{\ttt{Public :: Sensitivity}}\\
  \inference{}{\ttt{Secret :: Sensitivity}}\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
  \inference{%
    \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
  \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}
    {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    &\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    &\Gamma \vdash \ttt{f :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    & \Gamma \vdash \ttt{body :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}\\
    \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    \\ \Gamma,\ttt{(x :: Expr $\sigma$ $\tau$)} \vdash \ttt{rest :: Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; rest \}) :: Cmd $\alpha$}
  }\\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    \\ \Gamma \vdash \ttt{rest :: Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ c; rest \}) :: Cmd $\alpha$}
  }
\end{gather*}
\end{minipage}}
  \caption{Typing rules for sensitivity types}
\label{fig:SensTypes}
\end{figure}

@@

>>>>

\begin{figure}
  \centering
\resizebox{0.67\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
  \openup 3mm
\begin{gather*}
  \inference{}{\ttt{Public :: Sensitivity}}\\
  \inference{}{\ttt{Secret :: Sensitivity}}\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Int}}\\
  \inference{n \in \mathbb{N}}{\ttt{$n$ :: Expr $\sigma$ Int}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x + y :: Expr $\sigma$ Int}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ Int}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{x <? y :: Expr $\sigma$ Bool}}\\
  \inference{%
    \Gamma \vdash \ttt{a :: Expr $\sigma$ (Ptr $\tau$)}
    & \Gamma \vdash \ttt{i :: Expr $\sigma$ Int}}
    {\Gamma \vdash \ttt{a ! i :: Expr $\sigma$ $\tau$}}\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocPublic @$\tau$ n :: Cmd (Expr Public (Ptr $\tau$))}}\\
  \inference{\Gamma \vdash \ttt{n :: Int}}{\Gamma \vdash \ttt{allocSecret @$\tau$ n :: Cmd (Expr Secret (Ptr $\tau$))}}\\
  \inference{\Gamma \vdash \ttt{x :: $\tau$}}{\Gamma \vdash \ttt{decl x :: Cmd (Expr Public $\tau$)}}\\
  \inference{%
    \Gamma \vdash \ttt{x :: Expr $\sigma$ $\tau$}
    & \Gamma \vdash \ttt{y :: Expr $\sigma$ $\tau$}}
    {\Gamma \vdash \ttt{x .= y :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    \\ \Gamma \vdash \ttt{t :: Cmd $\alpha$}
    &\Gamma \vdash \ttt{f :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{ifThenElse cond t f :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{cond :: Expr $\sigma$ Bool}
    & \Gamma \vdash \ttt{body :: Cmd $\alpha$}}
    {\Gamma \vdash \ttt{while cond body :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{init :: Expr $\sigma$ $\tau$}\\
    \Gamma \vdash \ttt{fn :: Expr $\sigma$ $\tau$ $\rarr$ (Expr $\sigma$ Bool, Cmd (), Cmd ())}
    }{\Gamma \vdash \ttt{for init fn :: Cmd ()}}\\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    \\ \Gamma,\ttt{(x :: Expr $\sigma$ $\tau$)} \vdash \ttt{rest :: Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ x <- c; rest \}) :: Cmd $\alpha$}
  }\\
  \inference{%
    \Gamma \vdash \ttt{c :: Cmd (Expr $\sigma$ $\tau$)}
    \\ \Gamma \vdash \ttt{rest :: Cmd $\alpha$}
  }{%
    \Gamma \vdash \ttt{(\textbf{do} \{ c; rest \}) :: Cmd $\alpha$}
  }
\end{gather*}
\end{minipage}}
  \caption{Typing rules for sensitivity types}
\label{fig:SensTypes}
\end{figure}

@@

The implementation of the analysis tool is built around two primary data
structures:

\begin{itemize}
  \item
    A forest of multi-way trees (these are also called ``rose
trees''~\cite{LooplessBird}) which represents the leak paths
  \item
    A stack of name associations (a ``scope stack''). Each entry in the stack is
    a pair consisting of two lists of names. The first list contains all of the
    names that are in the current scope: the ``in-scope list''. When a
    conditional construct is entered, all of the secret variables in the
    conditional will be put into the second list and a new pair of empty lists
    will be pushed onto the stack. This second list is the ``secret list''
\end{itemize}

When a declaration is encountered, this name is added to the current ``scope
frame'' in the scope stack. Whenever an assignment is encountered, all of the
names in the left-hand side which are contained in the in-scope list of any
scope frame \textit{before} the current one are added as children (in the rose
tree forest) of all of nodes corresponding to the names in the secret list of
the stack frame in which the left-hand side name occured.

At the end of the algorithm, only leaves corresponding to public names are
retained.

% \begin{figure}
% \begin{lstlisting}[language=Haskell]
% analyze(forest, scope, return x) = forest
% analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
%   scope.insert(Public, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
%   scope.insert(Secret, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { n <- decl x; r n })) = do
%   scope.insert(Public, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { x .= y; r })) = do
%   let lhsNames = collectExprNames(x)
%   let rhsNames = collectExprNames(y)

%   foreach rhsName in rhsNames
%     if (rhsName is secret)
%       forest.addChildrenTo(rhsName, lhsNames)
%     end
%   end

%   foreach lhsName in lhsNames
%     let scopeFrame = scope.getScopeFrameOf(lhsName)

%     if scope.notCurrentScopeFrame(scopeFrame)
%       forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
%     end
%   end

%   analyze(forest, scope, r)

% analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
%   let secretNames = filter(isSecretName, collectExprNames(cond))

%   let tForest = copy(forest)
%   let fForest = copy(forest)
%   let tScope = copy(scope)
%   let fScope = copy(scope)

%   analyze(tForest, tScope.pushFrame(secretNames), r)
%   analyze(fForest, fScope.pushFrame(secretNames), r)

%   forest = union(tForest, fForest)
%   analyze(forest, scope, r)
% \end{lstlisting}
% \caption{Information leak analysis pseudocode}
% \end{figure}
